Normalization Performance Analysis for the Paired MSK Data Sets

### 2021-03-13 MSK_Data_Analysis.Rmd
Updated multiple plots and regenerated all results.

```{r analysis.settings}
settings <- list(
  # If true sets all other settings to TRUE
  all=F,
  # Application of the full DANA pipeline to the benchmark data
  bench.DANA=T,
  # Application of the full DANA pipeline to the test data
  test.DANA=T,
  # Generate interactive plots of co-expression structures
  investigate.coexpression=F,
  # Comparison of coexpression estimation methods
  compare.corr.methods=F,
  # Full Pipeline comparison of two correlation methods
  compare.two.methods=F,
  # Compare DANA results for different cutoff choices
  compare.cutoffs=T,
  # Perform Differential Expression Analysis for test and benchmark data sets
  perform.DEA=T,
  # Generate paper figures
  generate.paper.figs=T,
  # Specify if paper figures are exported
  export.figures = T,
  # Path for file exports
  paper.fig.path = "../danawriteup/figs/",
  # Clears environment
  debug=TRUE
)
if(settings$all) {
  settings$bench.DANA=TRUE
  settings$test.DANA=TRUE
  settings$investigate.coexpression=TRUE
  settings$compare.corr.methods=TRUE
  settings$compare.two.methods=TRUE
  settings$generate.paper.figs=TRUE
}
if(settings$generate.paper.figs) {
  settings$bench.DANA=TRUE
  settings$test.DANA=TRUE
}
if(settings$debug) rm(list=ls()[ls()!="settings"])
```

@@

  ## Display result statistics plot
  # MB (bic)
  p.test.mb.bic.stats <- plot.DANA.metrics(DANA.test.mb.bic.res$metrics, label.repel=TRUE) + ggtitle("mb (bic)")
  print(p.test.mb.bic.stats)
  # MB (aic)
  p.test.mb.aic.stats <- plot.DANA.metrics(DANA.test.mb.aic.res$metrics, label.repel=TRUE) + ggtitle("mb (aic)")
  print(p.test.mb.aic.stats)
  # MB (cv)
  p.test.mb.cv.stats <- plot.DANA.metrics(DANA.test.mb.cv.res$metrics, label.repel=TRUE) + ggtitle("mb (cv)")
  print(p.test.mb.cv.stats)
  # MB (av)
  p.test.mb.av.stats <- plot.DANA.metrics(DANA.test.mb.av.res$metrics, label.repel=TRUE) + ggtitle("mb (av)")
  print(p.test.mb.av.stats)
  # glasso (ric)
  p.test.glasso.ric.stats <- plot.DANA.metrics(DANA.test.glasso.ric.res$metrics, label.repel=TRUE) + ggtitle("glasso (ric)")
  print(p.test.glasso.ric.stats)
  # glasso (stars)
  p.test.glasso.stars.stats <- plot.DANA.metrics(DANA.test.glasso.stars.res$metrics, label.repel=TRUE) + ggtitle("glasso (stars)")
  print(p.test.glasso.stars.stats)
  # huge.mb (ric)
  p.test.huge.mb.ric.stats <- plot.DANA.metrics(DANA.test.huge.mb.ric.res$metrics, label.repel=TRUE) + ggtitle("huge.mb (ric)")
  print(p.test.huge.mb.ric.stats)
  # huge.mb (stars)
  p.test.huge.mb.stars.stats <- plot.DANA.metrics(DANA.test.huge.mb.stars.res$metrics, label.repel=TRUE) + ggtitle("huge.mb (stars)")
  print(p.test.huge.mb.stars.stats)
  # FastGGM
  p.test.fastggm.stats <- plot.DANA.metrics(DANA.test.fastggm.res$metrics, label.repel=TRUE) + ggtitle("FastGGM")
  print(p.test.fastggm.stats)
  # Pearson
  p.test.pearson.stats <- plot.DANA.metrics(DANA.test.pearson.res$metrics, label.repel=TRUE) + ggtitle("Pearson")
  print(p.test.pearson.stats)
  # Spearman
  p.test.spearman.stats <- plot.DANA.metrics(DANA.test.spearman.res$metrics, label.repel=TRUE) + ggtitle("Spearman")
  print(p.test.spearman.stats)

@@

  # Combined read count histogram for test and benchmark data
  df <- data.frame(bench=bench.RC.log2, test=test.RC.log2)
  p.RC.hist <- ggplot(df) + 
    theme_classic() +
    geom_histogram(aes(x=test, y=..count..,fill="#69b3a2"), binwidth = .1) +
    geom_histogram(aes(x=bench, y=-..count.., fill="#404080"), binwidth = .1) +
    geom_vline(xintercept = log2(config$t.zero+1), color="#5851b8", linetype="twodash") +
    geom_vline(xintercept = log2(config$t.poor+1), color="#5851b8", linetype="twodash") +
    geom_vline(xintercept = log2(config$t.well+1), color="#E7298A",  linetype="longdash") +
    geom_segment(aes(x = log2(config$t.zero+1), y = 75, xend = log2(config$t.poor+1), yend = 75),
                 arrow=arrow(length=unit(.07, "in"), ends="both"),
                 color="#5851b8") +
    annotate(geom="label", x=(log2(config$t.zero+1)+log2(config$t.poor+1))/2.0, y=84,
             label="neg. contr.", color="#5851b8", size=4, fill = alpha(c("white"),0.85), label.size = NA) +
    geom_segment(aes(x = log2(config$t.well+1), y = 75, xend = 10, yend = 75),
                 arrow=arrow(length=unit(.07, "in"), ends="last"),
                 color="#E7298A") +
    annotate(geom="label", x=log2(config$t.well+1)+.5, y=84,
             label="pos. contr.", color="#E7298A", size=4, hjust=0, fill = alpha(c("white"),0.85), label.size = NA) +
    # ylim(c(-90,90)) +
    scale_fill_manual(name="Data set",values=c("#404080", "#69b3a2"), labels=c("benchmark", "test"), guide = guide_legend(reverse=TRUE)) +
    # ggtitle("log2(Read count + 1)") +
    theme(legend.position=c(0.86,0.86), 
          # legend.title=element_blank(),
          legend.background=element_rect(fill=alpha('white', 0.9))) +
    scale_y_continuous(breaks=c(-50,0,50), labels=c(50,0,50), limits=c(-95,95)) +
    xlab("Mean") +
    ylab("Frequency")
    # theme(panel.border = element_blank(),
    #       axis.line = element_line(color = 'black'))
  print(p.RC.hist)
  rm(df)

@@

  # Negative controls
  p.corr.neg.bench <- ggplot.corr(corr.bench.neg, 
                                  clusters=clusters, 
                                  threshold=0, 
                                  title="benchmark (un-normalized)")
  p.corr.neg.test <- ggplot.corr(corr.test.neg, 
                                 clusters=clusters, 
                                 threshold=0, 
                                 title="test (un-normalized)")
  p.corr.neg.test.norm <- ggplot.corr(corr.test.norm.neg, 
                                     clusters=clusters, 
                                     threshold=0, 
                                     title="test (TMM)")

@@

  p.density.neg.nnz.freq <- ggplot(neg.corr, aes(x=corr, colour=control, linetype=control)) +
    geom_freqpoly(binwidth=.05, alpha=.8, size=.9) +
    theme_classic() +
    xlim(0, 1) +
    scale_linetype_manual(values=c("solid", "solid", "twodash"))+
    scale_color_manual(values=c('#1B9E77','#D95F02','#D95F02')) + # First 2 colors from rcolorbrewer set "Dark2"
    theme(legend.position=c(0.9,0.9), 
          legend.title=element_blank(),
          legend.background=element_rect(fill=alpha('white', 0.5))) +
    ylab("Frequency") +
    xlab("Marginal correlation") +
    ggtitle("Positive correlation among negative controls")
  print(p.density.neg.nnz.freq)

@@

  p.density.neg.nnz.freq <- ggplot(neg.corr, aes(x=corr, colour=control, linetype=control)) +
    geom_freqpoly(binwidth=.05, alpha=.8, size=.9) +
    theme_classic() +
    xlim(0, 1) +
    # scale_linetype_manual(values=c("twodash", "solid", "solid", "solid"))+
    scale_color_manual(values=c('#e7298a','#1B9E77','#D95F02', '#7570B3')) + # First colors from rcolorbrewer set "Dark2"
    theme(legend.position=c(0.9,0.86), 
          legend.title=element_blank(),
          legend.background=element_rect(fill=alpha('white', 0.5))) +
    ylab("Frequency") +
    xlab("Marginal correlation") #+ ggtitle("Positive correlation among negative controls")
  print(p.density.neg.nnz.freq)

@@

  p.cutoffs <-
    plot_grid(p.RC.conf1,
              p.RC.conf2 + labs(x="Mean", y=element_blank()),
              p.RC.conf3 + labs(x="Mean", y=element_blank()),
              p.meanvar.conf1,
              p.meanvar.conf2 + labs(x="Mean", y=element_blank()),
              p.meanvar.conf3 + labs(x="Mean", y=element_blank()),
              p.result.DANA.1,
              p.result.DANA.2 + labs(y=element_blank()),
              p.result.DANA.3 + labs(y=element_blank()),
              align="hv",
              labels=c("a","b","c"))
  print(p.cutoffs)

@@

```{r generate.paper.figs.compare.corr.methods}
if(settings$generate.paper.figs && settings$compare.corr.methods) { 
  methods.name <- c("mb (bic)", "mb (aic)", "mb (cv)","mb (av)", "glasso (ric)", "glasso (stars)", "huge.mb (ric)", "huge.mb (stars)", "fastggm", "pearson", "spearman")

  ## Between method correlation
  # Compute pearson correlation between cc+ for different methods
  compare.test.cc <- cbind(DANA.test.mb.bic.res$metrics$cc,
                           DANA.test.mb.aic.res$metrics$cc,
                           DANA.test.mb.cv.res$metrics$cc,
                           DANA.test.mb.av.res$metrics$cc,
                           DANA.test.glasso.ric.res$metrics$cc,
                           DANA.test.glasso.stars.res$metrics$cc,
                           DANA.test.huge.mb.ric.res$metrics$cc,
                           DANA.test.huge.mb.stars.res$metrics$cc,
                           DANA.test.fastggm.res$metrics$cc,
                           DANA.test.pearson.res$metrics$cc,
                           DANA.test.spearman.res$metrics$cc)
  rownames(compare.test.cc) <- rownames(DANA.test.mb.bic.res$metrics)
  colnames(compare.test.cc) <- methods.name
  p.pcorr.cc.corr <- corrplot.mixed(cor(compare.test.cc),lower="circle",upper="number")
  p.pcorr.cc.corr <- ggcorrplot(cor(compare.test.cc), type="upper", lab=TRUE)
  plot(p.pcorr.cc.corr)

  ## Display result statistics plot
  # MB (bic)
  p.test.mb.bic.stats <- plot.DANA.metrics(DANA.test.mb.bic.res$metrics, label.repel=TRUE, label.size = 2.5) + ggtitle("mb (bic)") + theme(plot.title = element_text(size=12))
  # MB (aic)
  p.test.mb.aic.stats <- plot.DANA.metrics(DANA.test.mb.aic.res$metrics, label.repel=TRUE, label.size = 2.5) + ggtitle("mb (aic)") + theme(plot.title = element_text(size=12))
  # MB (cv)
  p.test.mb.cv.stats <- plot.DANA.metrics(DANA.test.mb.cv.res$metrics, label.repel=TRUE, label.size = 2.5) + ggtitle("mb (cv)") + theme(plot.title = element_text(size=12))
  # MB (av)
  p.test.mb.av.stats <- plot.DANA.metrics(DANA.test.mb.av.res$metrics, label.repel=TRUE, label.size = 2.5) + ggtitle("mb (av)") + theme(plot.title = element_text(size=12))
  # glasso (ric)
  p.test.glasso.ric.stats <- plot.DANA.metrics(DANA.test.glasso.ric.res$metrics, label.repel=TRUE, label.size = 2.5) + ggtitle("glasso (ric)") + theme(plot.title = element_text(size=12))
  # glasso (stars)
  p.test.glasso.stars.stats <- plot.DANA.metrics(DANA.test.glasso.stars.res$metrics, label.repel=TRUE, label.size = 2.5) + ggtitle("glasso (stars)") + theme(plot.title = element_text(size=12))
  # huge.mb (ric)
  p.test.huge.mb.ric.stats <- plot.DANA.metrics(DANA.test.huge.mb.ric.res$metrics, label.repel=TRUE, label.size = 2.5) + ggtitle("huge.mb (ric)") + theme(plot.title = element_text(size=12))
  # huge.mb (stars)
  p.test.huge.mb.stars.stats <- plot.DANA.metrics(DANA.test.huge.mb.stars.res$metrics, label.repel=TRUE, label.size = 2.5) + ggtitle("huge.mb (stars)") + theme(plot.title = element_text(size=12))
  # FastGGM
  p.test.fastggm.stats <- plot.DANA.metrics(DANA.test.fastggm.res$metrics, label.repel=TRUE, label.size = 2.5) + ggtitle("FastGGM") + theme(plot.title = element_text(size=12))
  # Pearson
  p.test.pearson.stats <- plot.DANA.metrics(DANA.test.pearson.res$metrics, label.repel=TRUE, label.size = 2.5) + ggtitle("Pearson") + theme(plot.title = element_text(size=12))
  # Spearman
  p.test.spearman.stats <- plot.DANA.metrics(DANA.test.spearman.res$metrics, label.repel=TRUE, label.size = 2.5) + ggtitle("Spearman") + theme(plot.title = element_text(size=12))

  # Plot
  p.partialCorr.compare.metrics <-
    plot_grid(p.test.mb.bic.stats + labs(x="mcr-", y="cc+"),
              p.test.mb.aic.stats + labs(x="mcr-", y=element_blank()),
              p.test.mb.cv.stats + labs(x="mcr-", y=element_blank()),
              p.test.mb.av.stats + labs(x="mcr-", y="cc+"),
              p.test.glasso.ric.stats + labs(x="mcr-", y=element_blank()),
              p.test.glasso.stars.stats + labs(x="mcr-", y=element_blank()),
              p.test.huge.mb.ric.stats + labs(x="mcr-", y="cc+"),
              p.test.huge.mb.stars.stats + labs(x="mcr-", y=element_blank()),
              p.test.fastggm.stats + labs(x="mcr-", y=element_blank()),
              p.test.pearson.stats + labs(x="mcr-", y="cc+"),
              p.test.spearman.stats + labs(x="mcr-", y=element_blank()),
              ncol=3,
              align="hv")
  plot(p.partialCorr.compare.metrics)

  ## Correlation Plots
  p.corr.mb.bic <- ggplot.corr(DANA.test.mb.bic.res$data.model$pos$corr, clusters, title="mb (bic)")
  p.corr.mb.aic <- ggplot.corr(DANA.test.mb.aic.res$data.model$pos$corr, clusters, title="mb (aic)")
  p.corr.mb.cv <- ggplot.corr(DANA.test.mb.cv.res$data.model$pos$corr, clusters, title="mb (cv)")
  p.corr.mb.av <- ggplot.corr(DANA.test.mb.av.res$data.model$pos$corr, clusters, title="mb (av)")
  p.corr.glasso.ric <- ggplot.corr(DANA.test.glasso.ric.res$data.model$pos$corr, clusters, title="glasso (ric)")
  p.corr.glasso.stars <- ggplot.corr(DANA.test.glasso.stars.res$data.model$pos$corr, clusters, title="glasso (stars)")  
  p.corr.huge.mb.ric <- ggplot.corr(DANA.test.huge.mb.ric.res$data.model$pos$corr, clusters, title="huge.mb (ric)")
  p.corr.huge.mb.stars <- ggplot.corr(DANA.test.huge.mb.stars.res$data.model$pos$corr, clusters, title="huge.mb (stars)")
  p.corr.fastggm <- ggplot.corr(DANA.test.fastggm.res$data.model$pos$corr, clusters, title="FastGGM")
  p.corr.pearson <- ggplot.corr(DANA.test.pearson.res$data.model$pos$corr, clusters, title="Pearson")
  p.corr.spearman <- ggplot.corr(DANA.test.spearman.res$data.model$pos$corr, clusters, title="Spearman")

  # Plot
  p.partialCorr.compare.pcorrs <-
    plot_grid(p.corr.mb.bic + theme(legend.position="none"),
              p.corr.mb.aic + theme(legend.position="none"),
              p.corr.mb.cv + theme(legend.position="none"),
              p.corr.mb.av + theme(legend.position="none"),
              p.corr.glasso.ric + theme(legend.position="none"),
              p.corr.glasso.stars + theme(legend.position="none"),
              p.corr.huge.mb.ric + theme(legend.position="none"),
              p.corr.huge.mb.stars + theme(legend.position="none"),
              p.corr.fastggm + theme(legend.position="none"),
              p.corr.pearson + theme(legend.position="none"),
              p.corr.spearman + theme(legend.position="none"),
              get.legend(p.corr.mb.bic + theme(legend.position = "bottom")),
              ncol=3)
  plot(p.partialCorr.compare.pcorrs)

@@

>>>>

```{r analysis.settings}
settings <- list(
  # If true sets all other settings to TRUE
  all=F,
  # Application of the full DANA pipeline to the benchmark data
  bench.DANA=T,
  # Application of the full DANA pipeline to the test data
  test.DANA=T,
  # Generate interactive plots of co-expression structures
  investigate.coexpression=T,
  # Comparison of coexpression estimation methods
  compare.corr.methods=T,
  # Full Pipeline comparison of two correlation methods
  compare.two.methods=F,
  # Compare DANA results for different cutoff choices
  compare.cutoffs=T,
  # Perform Differential Expression Analysis for test and benchmark data sets
  perform.DEA=T,
  # Generate paper figures
  generate.paper.figs=T,
  # Specify if paper figures are exported
  export.figures = F,
  # Path for file exports
  paper.fig.path = "../danawriteup/figs/",
  # Clears environment
  debug=TRUE
)
if(settings$all) {
  settings$bench.DANA=TRUE
  settings$test.DANA=TRUE
  settings$investigate.coexpression=TRUE
  settings$compare.corr.methods=TRUE
  settings$compare.two.methods=TRUE
  settings$generate.paper.figs=TRUE
}
if(settings$generate.paper.figs) {
  settings$bench.DANA=TRUE
  settings$test.DANA=TRUE
}
if(settings$debug) rm(list=ls()[ls()!="settings"])
```

@@

  ## Display result statistics plot
  # MB (bic)
  p.test.mb.bic.stats <- plot.DANA.metrics(DANA.test.mb.bic.res$metrics, label.repel=TRUE) + ggtitle("MB (BIC)")
  print(p.test.mb.bic.stats)
  # MB (aic)
  p.test.mb.aic.stats <- plot.DANA.metrics(DANA.test.mb.aic.res$metrics, label.repel=TRUE) + ggtitle("MB (AIC)")
  print(p.test.mb.aic.stats)
  # MB (cv)
  p.test.mb.cv.stats <- plot.DANA.metrics(DANA.test.mb.cv.res$metrics, label.repel=TRUE) + ggtitle("MB (CV)")
  print(p.test.mb.cv.stats)
  # MB (av)
  p.test.mb.av.stats <- plot.DANA.metrics(DANA.test.mb.av.res$metrics, label.repel=TRUE) + ggtitle("MB (AV)")
  print(p.test.mb.av.stats)
  # glasso (ric)
  p.test.glasso.ric.stats <- plot.DANA.metrics(DANA.test.glasso.ric.res$metrics, label.repel=TRUE) + ggtitle("glasso (RIC)")
  print(p.test.glasso.ric.stats)
  # glasso (stars)
  p.test.glasso.stars.stats <- plot.DANA.metrics(DANA.test.glasso.stars.res$metrics, label.repel=TRUE) + ggtitle("glasso (StARS)")
  print(p.test.glasso.stars.stats)
  # huge.mb (ric)
  p.test.huge.mb.ric.stats <- plot.DANA.metrics(DANA.test.huge.mb.ric.res$metrics, label.repel=TRUE) + ggtitle("MB (RIC)")
  print(p.test.huge.mb.ric.stats)
  # huge.mb (stars)
  p.test.huge.mb.stars.stats <- plot.DANA.metrics(DANA.test.huge.mb.stars.res$metrics, label.repel=TRUE) + ggtitle("MB (StARS)")
  print(p.test.huge.mb.stars.stats)
  # FastGGM
  p.test.fastggm.stats <- plot.DANA.metrics(DANA.test.fastggm.res$metrics, label.repel=TRUE) + ggtitle("FastGGM")
  print(p.test.fastggm.stats)
  # Pearson
  p.test.pearson.stats <- plot.DANA.metrics(DANA.test.pearson.res$metrics, label.repel=TRUE) + ggtitle("Pearson")
  print(p.test.pearson.stats)
  # Spearman
  p.test.spearman.stats <- plot.DANA.metrics(DANA.test.spearman.res$metrics, label.repel=TRUE) + ggtitle("Spearman")
  print(p.test.spearman.stats)

@@

  # Combined read count histogram for test and benchmark data
  df <- data.frame(bench=bench.RC.log2, test=test.RC.log2)
  p.RC.hist <- ggplot(df) + 
    theme_classic() +
    geom_histogram(aes(x=test, y=..count..,fill="#69b3a2"), binwidth = .1) +
    geom_histogram(aes(x=bench, y=-..count.., fill="#404080"), binwidth = .1) +
    geom_vline(xintercept = log2(config$t.zero+1), color="#5851b8", linetype="twodash") +
    geom_vline(xintercept = log2(config$t.poor+1), color="#5851b8", linetype="twodash") +
    geom_vline(xintercept = log2(config$t.well+1), color="#E7298A",  linetype="longdash") +
    geom_segment(aes(x = log2(config$t.zero+1), y = 75, xend = log2(config$t.poor+1), yend = 75),
                 arrow=arrow(length=unit(.07, "in"), ends="both"),
                 color="#5851b8") +
    annotate(geom="label", x=(log2(config$t.zero+1)+log2(config$t.poor+1))/2.0, y=84,
             label="neg. contr.", color="#5851b8", size=4, fill = alpha(c("white"),0.85), label.size = NA) +
    geom_segment(aes(x = log2(config$t.well+1), y = 75, xend = 10, yend = 75),
                 arrow=arrow(length=unit(.07, "in"), ends="last"),
                 color="#E7298A") +
    annotate(geom="label", x=log2(config$t.well+1)+.5, y=84,
             label="pos. contr.", color="#E7298A", size=4, hjust=0, fill = alpha(c("white"),0.85), label.size = NA) +
    # ylim(c(-90,90)) +
    scale_fill_manual(name="Data set",values=c("#404080", "#69b3a2"), labels=c("benchmark", "test"), guide = guide_legend(reverse=TRUE)) +
    # ggtitle("log2(Read count + 1)") +
    theme(legend.position=c(0.86,0.86), 
          # legend.title=element_blank(),
          legend.background=element_rect(fill=alpha('white', 0.9))) +
    scale_y_continuous(breaks=c(-50,0,50), labels=c(50,0,50), limits=c(-95,95)) +
    xlab("Mean log2(read count)") +
    ylab("Frequency")
    # theme(panel.border = element_blank(),
    #       axis.line = element_line(color = 'black'))
  print(p.RC.hist)
  rm(df)

@@

  # Negative controls
  p.corr.neg.bench <- ggplot.corr(corr.bench.neg, 
                                  clusters=clusters, 
                                  threshold=0, 
                                  title="  benchmark (un-normalized)")
  p.corr.neg.test <- ggplot.corr(corr.test.neg, 
                                 clusters=clusters, 
                                 threshold=0, 
                                 title="  test (un-normalized)")
  p.corr.neg.test.norm <- ggplot.corr(corr.test.norm.neg, 
                                     clusters=clusters, 
                                     threshold=0, 
                                     title="  test (TMM)")

@@

  p.density.neg.nnz.freq <- ggplot(neg.corr, aes(x=corr, colour=control, linetype=control)) +
    geom_freqpoly(binwidth=.05, alpha=.8, size=.9) +
    theme_classic() +
    xlim(0, 1) +
    scale_linetype_manual(values=c("solid", "solid", "twodash"))+
    scale_color_manual(values=c('#1B9E77','#D95F02','#D95F02')) + # First 2 colors from rcolorbrewer set "Dark2"
    theme(legend.position=c(0.85,0.9), 
          legend.title=element_blank(),
          legend.background=element_rect(fill=alpha('white', 0.5))) +
    ylab("Frequency") +
    xlab("Marginal correlation") +
    ggtitle("Positive correlation among negative controls")
  print(p.density.neg.nnz.freq)

@@

  p.density.neg.nnz.freq <- ggplot(neg.corr, aes(x=corr, colour=control, linetype=control)) +
    geom_freqpoly(binwidth=.05, alpha=.8, size=.9) +
    theme_classic() +
    xlim(0, 1) +
    # scale_linetype_manual(values=c("twodash", "solid", "solid", "solid"))+
    scale_color_manual(values=c('#e7298a','#1B9E77','#D95F02', '#7570B3')) + # First colors from rcolorbrewer set "Dark2"
    theme(legend.position=c(0.85,0.86), 
          legend.title=element_blank(),
          legend.background=element_rect(fill=alpha('white', 0.5))) +
    theme(legend.key.width = unit(1.25,"cm")) +
    ylab("Frequency") +
    xlab("Marginal correlation") #+ ggtitle("Positive correlation among negative controls")
  print(p.density.neg.nnz.freq)

@@

  p.cutoffs <-
    plot_grid(p.RC.conf2,
              p.RC.conf1 + labs(x="Mean log2(read count)", y=element_blank()),
              p.RC.conf3 + labs(x="Mean log2(read count)", y=element_blank()),
              p.meanvar.conf2,
              p.meanvar.conf1 + labs(x="Mean log2(read count)", y=element_blank()),
              p.meanvar.conf3 + labs(x="Mean log2(read count)", y=element_blank()),
              p.result.DANA.2,
              p.result.DANA.1 + labs(y=element_blank()),
              p.result.DANA.3 + labs(y=element_blank()),
              align="hv",
              labels=c("a","b","c"))
  print(p.cutoffs)

@@

```{r generate.paper.figs.compare.corr.methods}
if(settings$generate.paper.figs && settings$compare.corr.methods) { 
  methods.name <- c("MB (BIC)", "MB (AIC)", "MB (CV)","MB (AV)", "MB (RIC)", "MB (StARS)", "glasso (RIC)", "glasso (StARS)", "FastGGM", "Pearson", "Spearman")

  ## Between method correlation
  # Compute pearson correlation between cc+ for different methods
  compare.test.cc <- cbind(DANA.test.mb.bic.res$metrics$cc,
                           DANA.test.mb.aic.res$metrics$cc,
                           DANA.test.mb.cv.res$metrics$cc,
                           DANA.test.mb.av.res$metrics$cc,
                           DANA.test.huge.mb.ric.res$metrics$cc,
                           DANA.test.huge.mb.stars.res$metrics$cc,
                           DANA.test.glasso.ric.res$metrics$cc,
                           DANA.test.glasso.stars.res$metrics$cc,
                           DANA.test.fastggm.res$metrics$cc,
                           DANA.test.pearson.res$metrics$cc,
                           DANA.test.spearman.res$metrics$cc)
  rownames(compare.test.cc) <- rownames(DANA.test.mb.bic.res$metrics)
  colnames(compare.test.cc) <- methods.name
  p.pcorr.cc.corr <- corrplot.mixed(cor(compare.test.cc),lower="circle",upper="number")
  p.pcorr.cc.corr <- ggcorrplot(cor(compare.test.cc), type="upper", lab=TRUE)
  plot(p.pcorr.cc.corr)

  ## Display result statistics plot
  # MB (bic)
  p.test.mb.bic.stats <- plot.DANA.metrics(DANA.test.mb.bic.res$metrics, label.repel=TRUE, label.size = 2.5) + ggtitle("MB (BIC)") + theme(plot.title = element_text(size=12))
  # MB (aic)
  p.test.mb.aic.stats <- plot.DANA.metrics(DANA.test.mb.aic.res$metrics, label.repel=TRUE, label.size = 2.5) + ggtitle("MB (AIC)") + theme(plot.title = element_text(size=12))
  # MB (cv)
  p.test.mb.cv.stats <- plot.DANA.metrics(DANA.test.mb.cv.res$metrics, label.repel=TRUE, label.size = 2.5) + ggtitle("MB (CV)") + theme(plot.title = element_text(size=12))
  # MB (av)
  p.test.mb.av.stats <- plot.DANA.metrics(DANA.test.mb.av.res$metrics, label.repel=TRUE, label.size = 2.5) + ggtitle("MB (AV)") + theme(plot.title = element_text(size=12))
  # huge.mb (ric)
  p.test.huge.mb.ric.stats <- plot.DANA.metrics(DANA.test.huge.mb.ric.res$metrics, label.repel=TRUE, label.size = 2.5) + ggtitle("MB (RIC)") + theme(plot.title = element_text(size=12))
  # huge.mb (stars)
  p.test.huge.mb.stars.stats <- plot.DANA.metrics(DANA.test.huge.mb.stars.res$metrics, label.repel=TRUE, label.size = 2.5) + ggtitle("MB (StARS)") + theme(plot.title = element_text(size=12))
  # glasso (ric)
  p.test.glasso.ric.stats <- plot.DANA.metrics(DANA.test.glasso.ric.res$metrics, label.repel=TRUE, label.size = 2.5) + ggtitle("glasso (RIC)") + theme(plot.title = element_text(size=12))
  # glasso (stars)
  p.test.glasso.stars.stats <- plot.DANA.metrics(DANA.test.glasso.stars.res$metrics, label.repel=TRUE, label.size = 2.5) + ggtitle("glasso (StARS)") + theme(plot.title = element_text(size=12))
  # FastGGM
  p.test.fastggm.stats <- plot.DANA.metrics(DANA.test.fastggm.res$metrics, label.repel=TRUE, label.size = 2.5) + ggtitle("FastGGM") + theme(plot.title = element_text(size=12))
  # Pearson
  p.test.pearson.stats <- plot.DANA.metrics(DANA.test.pearson.res$metrics, label.repel=TRUE, label.size = 2.5) + ggtitle("Pearson") + theme(plot.title = element_text(size=12))
  # Spearman
  p.test.spearman.stats <- plot.DANA.metrics(DANA.test.spearman.res$metrics, label.repel=TRUE, label.size = 2.5) + ggtitle("Spearman") + theme(plot.title = element_text(size=12))

  # Plot
  p.partialCorr.compare.metrics <-
    plot_grid(p.test.mb.bic.stats + labs(x="mcr-", y="cc+"),
              p.test.mb.aic.stats + labs(x="mcr-", y=element_blank()),
              p.test.mb.cv.stats + labs(x="mcr-", y=element_blank()),
              p.test.mb.av.stats + labs(x="mcr-", y="cc+"),
              p.test.huge.mb.ric.stats + labs(x="mcr-", y=element_blank()),
              p.test.huge.mb.stars.stats + labs(x="mcr-", y=element_blank()),
              p.test.glasso.ric.stats + labs(x="mcr-", y="cc+"),
              p.test.glasso.stars.stats + labs(x="mcr-", y=element_blank()),
              p.test.fastggm.stats + labs(x="mcr-", y=element_blank()),
              p.test.pearson.stats + labs(x="mcr-", y="cc+"),
              p.test.spearman.stats + labs(x="mcr-", y=element_blank()),
              ncol=3,
              align="hv")
  plot(p.partialCorr.compare.metrics)

  ## Correlation Plots
  p.corr.mb.bic <- ggplot.corr(DANA.test.mb.bic.res$data.model$pos$corr, clusters, title="MB (BIC)")
  p.corr.mb.aic <- ggplot.corr(DANA.test.mb.aic.res$data.model$pos$corr, clusters, title="MB (AIC)")
  p.corr.mb.cv <- ggplot.corr(DANA.test.mb.cv.res$data.model$pos$corr, clusters, title="MB (CV)")
  p.corr.mb.av <- ggplot.corr(DANA.test.mb.av.res$data.model$pos$corr, clusters, title="MB (AV)")
  p.corr.huge.mb.ric <- ggplot.corr(DANA.test.huge.mb.ric.res$data.model$pos$corr, clusters, title="MB (RIC)")
  p.corr.huge.mb.stars <- ggplot.corr(DANA.test.huge.mb.stars.res$data.model$pos$corr, clusters, title="MB (StARS)")
  p.corr.glasso.ric <- ggplot.corr(DANA.test.glasso.ric.res$data.model$pos$corr, clusters, title="glasso (RIC)")
  p.corr.glasso.stars <- ggplot.corr(DANA.test.glasso.stars.res$data.model$pos$corr, clusters, title="glasso (StARS)")  
  p.corr.fastggm <- ggplot.corr(DANA.test.fastggm.res$data.model$pos$corr, clusters, title="FastGGM")
  p.corr.pearson <- ggplot.corr(DANA.test.pearson.res$data.model$pos$corr, clusters, title="Pearson")
  p.corr.spearman <- ggplot.corr(DANA.test.spearman.res$data.model$pos$corr, clusters, title="Spearman")

  # Plot
  p.partialCorr.compare.pcorrs <-
    plot_grid(p.corr.mb.bic + theme(legend.position="none"),
              p.corr.mb.aic + theme(legend.position="none"),
              p.corr.mb.cv + theme(legend.position="none"),
              p.corr.mb.av + theme(legend.position="none"),
              p.corr.huge.mb.ric + theme(legend.position="none"),
              p.corr.huge.mb.stars + theme(legend.position="none"),
              p.corr.glasso.ric + theme(legend.position="none"),
              p.corr.glasso.stars + theme(legend.position="none"),
              p.corr.fastggm + theme(legend.position="none"),
              p.corr.pearson + theme(legend.position="none"),
              p.corr.spearman + theme(legend.position="none"),
              get.legend(p.corr.mb.bic + theme(legend.position = "bottom")),
              ncol=3)
  plot(p.partialCorr.compare.pcorrs)

@@

## Arrange plots for paper

```{r generate.paper.figs.arrange.for.paper}
if(settings$generate.paper.figs) { 
  top.row <-
    plot_grid(NULL,
              p.corr.pos.three,
              NULL,
              labels=c("", ""),
              rel_heights = c(0.5 ,10, 0.2),
              ncol=1)
  bottom.row <- 
    plot_grid(NULL,
              p.scatter.test.TMM,
              p.scatter.test.UQ,
              NULL,
              align="h",
              labels=c("", "b", "", ""),
              vjust = 0,
              rel_widths = c(1,2.5,2.5,1),
              nrow=1)
  p.results.paper <- 
    plot_grid(top.row, 
              bottom.row,
              # align="h",
              labels=c("a", ""),
              rel_heights = c(5,3.5),
              ncol=1)
  plot(p.results.paper)

  if(settings$export.figures) {
    ggsave(paste0(settings$paper.fig.path, "MSK_posCorr_results.pdf"), p.results.paper, width=8, height=6.5, device="pdf")
  }
}
```
